### 2004-06-28 doc/Simulation_and_Control_using_Supremica/functionblocks.tex
*** empty log message ***

\begin{bf}
{This chapter is copied from Sachin Jain MSc Thesis}
\end{bf}

@@

\section{EMBench and Function Blocks}

Since the FBEditor provided the aforementioned functionality, it
was decided that the EMBench should leverage it. In particular,
the bench relies on the editor for two basic features.
\begin{enumerate}
\item To generate the Java files from the IEC 61499 source files.
\item To manage the Java thread that initializes the blocks during
simulation.
\end{enumerate}

It has been visualized that the bench will eventually have the
editor as one of its components. The bench explicitly manages the
design activities of the user and generates the function block
definitions for the user design. It then requests the FBEditor
component to load the specified source files, generate the Java
classes and run the simulation. In addition, the user may make
behavioral changes to the blocks by editing the events, if he/she
so desires. The editor conforms to the published service
specifications of the bench as explained in chapter \ref{chap3}
and hence would present the same interface to the client.

Currently, however, the FBEditor is not a part of the bench
because it does not expose an API. Since it is external to the
bench, the bench has to circumvent this problem by allowing the
editor to be executed as a separate application and delegating the
simulation task completely to the editor. The data exchange
necessary between the two applications is handled via network
communication. This issue is explained in a greater detail in
chapter~\ref{chap4} and chapter~\ref{chap5}.

>>>>

\begin{bf}
{This chapter is with minor revisions copied from chapter 2 in \cite{j:des:2002}.}
\end{bf}

@@

%\section{EMBench and Function Blocks}

%Since the FBEditor provided the aforementioned functionality, it
%was decided that the EMBench should leverage it. In particular,
%the bench relies on the editor for two basic features.
%\begin{enumerate}
%\item To generate the Java files from the IEC 61499 source files.
%\item To manage the Java thread that initializes the blocks during
%simulation.
%\end{enumerate}

%It has been visualized that the bench will eventually have the
%editor as one of its components. The bench explicitly manages the
%design activities of the user and generates the function block
%definitions for the user design. It then requests the FBEditor
%component to load the specified source files, generate the Java
%classes and run the simulation. In addition, the user may make
%behavioral changes to the blocks by editing the events, if he/she
%so desires. The editor conforms to the published service
%specifications of the bench as explained in chapter \ref{chap3}
%and hence would present the same interface to the client.

%Currently, however, the FBEditor is not a part of the bench
%because it does not expose an API. Since it is external to the
%bench, the bench has to circumvent this problem by allowing the
%editor to be executed as a separate application and delegating the
%simulation task completely to the editor. The data exchange
%necessary between the two applications is handled via network
%communication. This issue is explained in a greater detail in
%chapter~\ref{chap4} and chapter~\ref{chap5}.
